Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-28 writing/DraftExposurePaper/DraftExposurePaper.Rmd
work on code to pull data for all ike_fips available

```{r echo = FALSE, fig.height = 4, fig.width = 6}
library(weathermetrics)
#library(data.table)
#ike_gauge <- read.csv("/Users/joshuaferreri/Documents/ike_rain.csv", header = TRUE)
#save(ike_gauge, file = "writing/DraftExposurePaper/ike_gauge.RData")
#load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/ike_gauge.RData")
load("ike_gauge.RData")
ike_gauge$rain_mm <- convert_precip(ike_gauge$rain_in, 
                                    "inches", "mm")
ike_nldas <- county_rain(counties = unique(ike_gauge$fips),
                             start_year = 2008, end_year = 2008,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
ike_nldas <- ike_nldas %>%
        filter(storm_id == "Ike-2008")
ike_gauge$fips <- as.character(ike_gauge$fips)
compare_rain1 <- right_join(ike_nldas, ike_gauge, by = "fips")
#ike_nldas <- as.data.table(alex_nldas)
#ike_gauge <- as.data.table(alex_gauge)
#compare_rain1 <- left_join(alex_nldas, alex_gauge, by = "fips")
b <- ggplot(compare_rain1, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
b
```

@@

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain1 %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)") + 
        scale_color_manual(values = c("blue", "black"), guide = "none") 
```

@@

```{r}
my_fips <- ike_fips[1:3]
my_stations <- NA
test <- expand.grid(my_fips, my_stations)
colnames(test) <- c("fips", "station")
for(fips in my_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        test[test$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
} #This works fine (small subset of code below)
ike_table <- expand.grid(ike_fips, my_stations)
colnames(ike_table) <- c("fips", "station")
#for(fips in ike_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)
} #getting error
```

>>>>

```{r echo = FALSE, fig.height = 4, fig.width = 6}
library(weathermetrics)
#library(data.table)
#ike_gauge <- read.csv("/Users/joshuaferreri/Documents/ike_rain.csv", header = TRUE)
#save(ike_gauge, file = "writing/DraftExposurePaper/ike_gauge.RData")
#load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/ike_gauge.RData")
load("ike_gauge.RData")
ike_gauge$rain_mm <- convert_precip(ike_gauge$rain_in, 
                                    "inches", "mm")
ike_nldas <- county_rain(counties = unique(ike_gauge$fips),
                             start_year = 2008, end_year = 2008,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
ike_nldas <- ike_nldas %>%
        filter(storm_id == "Ike-2008")
ike_gauge$fips <- as.character(ike_gauge$fips)
compare_rain <- right_join(ike_nldas, ike_gauge, by = "fips")
#ike_nldas <- as.data.table(alex_nldas)
#ike_gauge <- as.data.table(alex_gauge)
#compare_rain1 <- left_join(alex_nldas, alex_gauge, by = "fips")
b <- ggplot(compare_rain1, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
b
```

@@

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)") + 
        scale_color_manual(values = c("blue", "black"), guide = "none") 
```

@@

```{r}
my_fips <- ike_fips[c(1:6, 10, 13:16, 18, 20:25, 28:29, 31, 33:34, 36:40, 42, 44:45)]
my_stations <- NA
ike_table <- expand.grid(my_fips, my_stations)
colnames(ike_table) <- c("fips", "station")
for(fips in my_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
} #This works fine (small subset of the code below)
my_fips <- ike_fips[44:45]
my_stations <- NA
test_2 <- expand.grid(my_fips, my_stations)
colnames(test_2) <- c("fips", "station")
for(fips in my_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        test_2[test_2$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
}
#Do not work: 7, 8, 9, 11, 12, 17, 19, 26, 27, 30, 32,35, 41, 43, 
ike_table <- ike_table %>%
        arrange(desc(station)) %>%
        slice(1:15)
ike_table <- expand.grid(ike_fips, my_stations)
colnames(ike_table) <- c("fips", "station")
#for(fips in ike_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)
} #getting error
```
